The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-04 hw1/paper/main.tex
adjust the layout
Update main.tex

  \bf{naive Bayes classifier}:

>>>>

  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most likely outcome according to the conditional probability it just recorded.
